Efficient ancestry and mutation simulation with msprime 1.0

### 2021-12-05 paper.tex
Arrange Figure 5 vertically.

\begin{figure*}
    \includegraphics{illustrations/mutated_tree}
    \caption{
        \label{fig-mutated-trees}
        Visualization of the separation between ancestry and mutation
        simulation. (A) The result of an invocation of \texttt{sim\_ancestry}
        is two trees along a 1kb chunk of genome relating three diploid samples.
        Each diploid individual consists of two genomes (or nodes), indicated
        by color.
        (B) This ancestry is provided as the input to \texttt{sim\_mutations},
        which adds mutations.
        Graphics produced using \tskit's \texttt{draw\_svg} method.
    }
\end{figure*}

@@

\begin{figure*}
\begin{subfigure}[t]{0.33\textwidth}
\centering
\caption*{(A)}
    \begin{tikzpicture}[scale=0.45,nodestyle/.style={font=\scriptsize}]

    \draw (-2,0) -- (-2,3) -- (0, 3);
    \draw (1,0) -- (1,1);
    \draw (0,1) -- (2,1) -- (2,2) -- (4,2) -- (4,0);
    \draw (3,2) -- (3,5);
    \draw (0,1) -- (0,3);
    \draw (-1, 3) -- (-1, 5) -- (3,5);

    \draw[fill] (-2,0) circle [radius=0.05];
    \draw[fill] (-1,3) circle [radius=0.05];
    \draw[fill] (1,0) circle [radius=0.05];
    \draw[fill] (4,0) circle [radius=0.05];
    \draw[fill] (1,1) circle [radius=0.05];
    \draw[fill] (3,2) circle [radius=0.05];
    \draw[fill] (1,5) circle [radius=0.05];

    \node[nodestyle] [below] at (-2,0) {0};
    \node[nodestyle] [below] at (1,0) {1};
    \node[nodestyle] [below] at (4,0) {2};
    \node[nodestyle] [above] at (1,1) {3};
    \node[nodestyle] [below right] at (1,1) {$x = 0.3$};
    \node[nodestyle] [above right] at (3,2) {4};
    \node[nodestyle] [above left] at (-1,3) {5};
    \node[nodestyle] [above] at (1,5) {6};

    \end{tikzpicture}
\end{subfigure}
\begin{subfigure}[t]{0.33\textwidth}
\centering
\caption*{(B)}
\begin{tikzpicture}[node distance=2mm and 4mm,scale=0.45]

\tikzset{greynode/.style={circle,fill,inner sep=0.7},
nodelabel/.style={font=\scriptsize}}

@@

% Right sample nodes
\node (rightTree) at (4, 0) {};
\node [greynode] (s0r) at ($(s0) + (rightTree)$) {};
\node [greynode] (s1r) at ($(s1) + (rightTree)$) {};
\node [greynode] (s2r) at ($(s2) + (rightTree)$) {};
\foreach \u/\lab in {s0r/0, s1r/1, s2r/2} \node[nodelabel,anchor=north] at (\u) {\lab};

@@

% Axes
\draw[very thick] ($(s0) + (0,-1.0)$) -- ($(s2r) + (0,-1.0)$);
\node (topAx) at (0,-1.0) {};
\node (topLeft) at ($(s0) + (0,-1.0)$) {};
\node (genUnit) at ($0.1*(s2r) - 0.1*(s0)$) {};
\foreach \x in {0, 5, 10} \draw ($(topLeft) + \x*(genUnit) + (0,0.1)$) -- +(0, -0.2); % tick marks
\node[anchor=north] at ($(topLeft)$) {\scriptsize 0.0};
\node[anchor=north] at ($(topLeft) + 5*(genUnit)$) {\scriptsize 0.3};
\node[anchor=north] at ($(topLeft) + 10*(genUnit)$) {\scriptsize 1.0};

@@

% Axis titles
\node (topLabel) at ($(topLeft) + 5*(genUnit) + (0,-1.3)$) {$\scriptsize\textrm{Genome position}$};
\end{tikzpicture}
\end{subfigure}
\begin{subfigure}[t]{0.33\textwidth}
\centering
\caption*{(C)}
\begin{tikzpicture}[node distance=2mm and 4mm,scale=0.45]

\tikzset{greynode/.style={circle,fill,inner sep=0.7},
nodelabel/.style={font=\scriptsize}}

@@

% Axes
\draw[very thick] ($(s0) + (0,-1.0)$) -- ($(s2r) + (0,-1.0)$);
\node (topAx) at (0,-1.0) {};
\node (topLeft) at ($(s0) + (0,-1.0)$) {};
\node (genUnit) at ($0.1*(s2r) - 0.1*(s0)$) {};
\foreach \x in {0, 5, 10} \draw ($(topLeft) + \x*(genUnit) + (0,0.1)$) -- +(0, -0.2); % tick marks
\node[anchor=north] at ($(topLeft)$) {\scriptsize 0.0};
\node[anchor=north] at ($(topLeft) + 5*(genUnit)$) {\scriptsize 0.3};
\node[anchor=north] at ($(topLeft) + 10*(genUnit)$) {\scriptsize 1.0};

@@

% Axis titles
\node (topLabel) at ($(topLeft) + 5*(genUnit) + (0,-1.3)$) {$\scriptsize\textrm{Genome position}$};
\end{tikzpicture}
\end{subfigure}
\caption{\label{fig-arg} (A) A simple ARG in which a recombination
occurs at position 0.3; (B) the equivalent topology depicted as a tree
sequence, including the recombination node; (C) the same tree sequence
topology ``simplified'' down to its minimal tree sequence representation.
Note that the internal nodes have been renumbered in the simplified
representation, so that, e.g., node 5 in (C) corresponds to node 6 in
(A) and (B).}
\end{figure*}

>>>>

\begin{figure*}
    \begin{center}
    \includegraphics{illustrations/mutated_tree}
    \end{center}
    \caption{
        \label{fig-mutated-trees}
        Visualization of the separation between ancestry and mutation
        simulation. (A) The result of an invocation of \texttt{sim\_ancestry}
        is two trees along a 1kb chunk of genome relating three diploid samples.
        Each diploid individual consists of two genomes (or nodes), indicated
        by color.
        (B) This ancestry is provided as the input to \texttt{sim\_mutations},
        which adds mutations.
        Graphics produced using \tskit's \texttt{draw\_svg} method.
    }
\end{figure*}

@@

\begin{figure}

\newcommand\subfigtextsize{\small}
\begin{subfigure}{\columnwidth}
\centering
\caption*{(A)}
    \begin{tikzpicture}[xscale=0.8, yscale=0.4, node distance=2mm and 30mm]

\tikzset{greynode/.style={circle,fill,inner sep=1},
nodelabel/.style={font=\subfigtextsize}}

\node (s0) [greynode] {};
\node (s1) [right=of s0,greynode] {};
\node (s2) [right=of s1,greynode] {};
\node [greynode] (s3) at ($(s1) + (0,1)$) {};
\node [greynode] (s4) at ($0.5*(s1) + 0.5*(s2) + (0,2)$) {};
\node [greynode] (s5) at ($0.5*(s0) + 0.5*(s1) + (0,3)$) {};
\node [greynode] (s6) at ($(s1) + (0,5)$) {};

\node [nodelabel,anchor=north west] at ($(s3) + (0,0)$) {$x = 0.3$};
\foreach \u/\lab in {s0/0, s1/1, s2/2} \node[nodelabel,anchor=north] at (\u) {\lab};
\foreach \u/\lab in {s4/4} \node[nodelabel,anchor=south west] at (\u) {\lab};
\foreach \u/\lab in {s5/5} \node[nodelabel,anchor=south east] at (\u) {\lab};
\foreach \u/\lab in {s3/3, s6/6} \node[nodelabel,anchor=south] at (\u) {\lab};

%% Edges
\draw (s1) -- (s3);
\foreach \child/\parent in {s6/s5, s6/s4, s5/s0, s4/s2}
	\draw (\child) -| (\parent);

\draw (s5) -| ($0.5*(s3) + 0.5*(s3-|s5)$) |- (s3);
\draw (s4) -| ($0.5*(s3) + 0.5*(s3-|s4)$) |- (s3);

\end{tikzpicture}
\end{subfigure}\\
\begin{subfigure}{\columnwidth}
\centering
\caption*{(B)}
\begin{tikzpicture}[xscale=0.8, yscale=0.2, node distance=2mm and 10mm]

\tikzset{greynode/.style={circle,fill,inner sep=1},
nodelabel/.style={font=\subfigtextsize}}

@@

% Right sample nodes
\node (rightTree) at (5, 0) {};
\node [greynode] (s0r) at ($(s0) + (rightTree)$) {};
\node [greynode] (s1r) at ($(s1) + (rightTree)$) {};
\node [greynode] (s2r) at ($(s2) + (rightTree)$) {};
\foreach \u/\lab in {s0r/0, s1r/1, s2r/2} \node[nodelabel,anchor=north] at (\u) {\lab};

@@

% Axes
\draw[very thick] ($(s0) + (0,-2.5)$) -- ($(s2r) + (0,-2.5)$);
\node (topAx) at (0,-1.0) {};
\node (topLeft) at ($(s0) + (0,-2.5)$) {};
\node (genUnit) at ($0.1*(s2r) - 0.1*(s0)$) {};
\foreach \x in {0, 5, 10} \draw ($(topLeft) + \x*(genUnit) + (0,0.1)$) -- +(0, -0.2); % tick marks
\node[anchor=north] at ($(topLeft)$) {\subfigtextsize 0.0};
\node[anchor=north] at ($(topLeft) + 5*(genUnit)$) {\subfigtextsize 0.3};
\node[anchor=north] at ($(topLeft) + 10*(genUnit)$) {\subfigtextsize 1.0};

@@

% Axis titles
\node (topLabel) at ($(topLeft) + 5*(genUnit) + (0,-3.0)$) {$\subfigtextsize\textrm{Genome position}$};
\end{tikzpicture}
\end{subfigure}\\
\begin{subfigure}{\columnwidth}
\centering
\caption*{(C)}
\begin{tikzpicture}[xscale=0.8, yscale=0.2, node distance=2mm and 10mm]

\tikzset{greynode/.style={circle,fill,inner sep=1},
nodelabel/.style={font=\subfigtextsize}}

@@

% Axes
\draw[very thick] ($(s0) + (0,-2.0)$) -- ($(s2r) + (0,-2.0)$);
\node (topAx) at (0,-1.0) {};
\node (topLeft) at ($(s0) + (0,-2.0)$) {};
\node (genUnit) at ($0.1*(s2r) - 0.1*(s0)$) {};
\foreach \x in {0, 5, 10} \draw ($(topLeft) + \x*(genUnit) + (0,0.1)$) -- +(0, -0.2); % tick marks
\node[anchor=north] at ($(topLeft)$) {\subfigtextsize 0.0};
\node[anchor=north] at ($(topLeft) + 5*(genUnit)$) {\subfigtextsize 0.3};
\node[anchor=north] at ($(topLeft) + 10*(genUnit)$) {\subfigtextsize 1.0};

@@

% Axis titles
\node (topLabel) at ($(topLeft) + 5*(genUnit) + (0,-3.0)$) {$\subfigtextsize\textrm{Genome position}$};
\end{tikzpicture}
\end{subfigure}
\caption{\label{fig-arg} (A) A simple ARG in which a recombination
occurs at position 0.3; (B) the equivalent topology depicted as a tree
sequence, including the recombination node; (C) the same tree sequence
topology ``simplified'' down to its minimal tree sequence representation.
Note that the internal nodes have been renumbered in the simplified
representation, so that, e.g., node 5 in (C) corresponds to node 6 in
(A) and (B).}
\end{figure}
